CODECHECK: An Open Science initiative for the independent execution of computations underlying research articles during peer review improves reproducibility

### 2021-02-09 codecheck-paper.tex
bye bye footnotes, remove manual page breaks

Given that no clear standards yet exist for sharing data, what hope might there be for sharing computer programs?
Both data and software are required to validate a
computational analysis; data can be seen as inert whereas
code requires an environment to be run in.
This makes software harder to share.
Our experience is that researchers offer several reasons for why code
is not shared, e.g.,~``there is no documentation'', ``I cannot maintain it'', or ``I do not want to give away my code to competitors''.
Our view is that sharing code, wherever possible, is good for the community and the individual \cite{Barnes2010-iv,markowetz_five_2015}.
Having code and data openly available and archived provides a valuable
resource for others to learn from, even if the code is broken or lacks documentation.
However, with a little effort, we believe that if an independent person can execute an analysis, this is worth documenting and that this  reduces the barrier to evaluating non-text research materials.
Just as data journals' validations of data and all journals' peer review  provides a ``baseline reassurance'', i.e.,~that a paper has been checked by someone with an understanding of the topic \cite{fyfe_mission_2019}, the same baseline could be provided for the workflow underlying a paper.
With this in mind, we have developed a set of principles and an example workflow that provides a pragmatic way of checking that a paper's code works.

Here we offer a thorough description of a process and its variations to integrate a much-needed evaluation of computational reproducibility\footnote{Following the Claerbout/Donoho/Peng terminology, see \cite{barba_terminologies_2018}.} into peer review, and we demonstrate its feasibility by means of 25 reproductions across scientific disciplines.
We call this system CODECHECK.

@@

\textbf{Step 3:} The CODECHECKER runs the code, based on instructions provided by
the author. They check if some or all of the results from the paper can be
reproduced. If there are
any problems running the code, the CODECHECKER asks the AUTHOR for help,
updates, or further documentation.
The burden to provide reproducible material lies with the author.
The CODECHECKER then tries to run the code again.
This process iterates until either the CODECHECKER is successful,
or the CODECHECKER concludes the code can not be executed within the context of a CODECHECK.
As part of this process, the CODECHECKER could work entirely locally, relying on their own computing resources, or in the cloud, e.g.,~using the open MyBinder infrastructure \cite{jupyter_binder_2018} or alternatives, some of which are more tailored to scientific publications while others offer commercial options for, e.g.,~publishers (cf. \cite{konkol_publishing_2020}).
A cloud-based infrastructure allows for the CODECHECKER and author to collaboratively improve the code and enforces a complete definition of the computing environment; but, unless secure infrastructure is provided, e.g.,~by the PUBLISHER, this requires the code and data to be published openly online.
Note that the task of the CODECHECKER is to check the ``mechanics'' of the workflow not to evaluate its correctness. 
In the context of mathematics, Stodden et~al. \cite{stodden_setting_2013} distinguish between \emph{verification} and \emph{validation};
following their definition, a CODECHECK ensures verification
\footnote{Note this is a different use from that referred to as the \emph{Verification Reports} article type in the journal \emph{Cortex} \cite{chambers_verification_2020}.},
of computational results, i.e.,~checking that the code correctly produces the output it claims to create, but not a validation, i.e.,~checking that the code implements the right algorithm to solve the specific research problem.
Nevertheless, simply attempting to reproduce an output may highlight a submission's shortcomings in meeting a journal's requirements (cf.~\cite{christian_journal_2020}) and may effectively increase transparency, thereby improving practices (cf.~\cite{nosek_scientific_2012}) even if the check does not go into every detail.

@@

\textbf{Step 6:} The PUBLISHER can, depending on the timing, provide the
certificate to peer-reviewers or handling editors or publish it
and link between  certificate, paper, and any repositories 
through metadata. Currently, the CODECHECKER creates these connections on
Zenodo\footnote{
See ``related identifiers'' and ``alternate identifiers'' in the right-hand
sidebar of certificate \texttt{2020-025} \cite{cert-2020-025}.}.
The PUBLISHER also credits the CODECHECKER for their work by depositing
the activity appropriately in scholarly profiles, such as ORCID\footnote{
See peer review contributions in ORCID records at
\url{https://support.orcid.org/hc/en-us/articles/360006971333-Peer-Review}.}.
The PUBLISHER also ensures proper publication metadata, e.g.,~links from the 
certificate repository to the published paper or the original code repository.

\newpage

@@

We also see a great opportunity to involve \emph{early-career researchers} (ECRs) as codecheckers.
ECRs arguably have a high interest in learning
about the latest tools and technologies, as they build up their own
expertise and specialisation.
CODECHECK offers a way for ECRs to gain insights into new research and
highlight the importance of reproduction.  
\emph{ReScience X}, a journal devoted to reproduction and replication experiments \cite{roesch_new_2020}, shares an interest in this combination.
ECRs are also often familiar with new technologies, thus also making them likely to author CODECHECK-ready manuscripts
\footnote{Cf. the 77\% of 141 registered reports that were submitted to leading Neuroscience journals by ECRs \cite{chambers_registered_2019}.}.
As ECRs are introduced to peer review as codecheckers, they may transition into the role of scientific reviewer over time.
Overall, we see several opportunities and benefits to setting up a new process for CODECHECKING with a clear commitment to openness and transparency, independent of the current peer review process (see \emph{Openness} dimension).

The codechecker could be a member of \textbf{editorial staff}; this is
the most controlled but also resource-intensive option.  Such a
resource commitment would show that publishers are investing in
reproducibility, yet this commitment may be hard for small publishers.
These codecheckers could be fully integrated into internal workflows.
Credit for doing the codecheck is also achieved, as it is part of
their duties.  By contrast, it is useful for researchers to be
publicly credited for their reviewing activity.  A regular review
may be listed in public databases (e.g.,~ORCID
\footnote{\href{https://support.orcid.org/hc/en-us/articles/360006971333-Peer-Review}{https://support.orcid.org/hc/en-us/articles/360006971333-Peer-Review}}
or commercial offerings such as Publons
\footnote{\href{https://publons.com/}{https://publons.com/}} or
ReviewerCredits\footnote{\href{https://www.reviewercredits.com/}{https://www.reviewercredits.com/}});
a codechecker could be similarly listed.
% The number of scientific reviews is of course only a coarse indicator of an individual's community contribution, yet it is unclear if a regular reviewer, who conducts a regular scientific review and in addition also conducts a CODECHECK, should be credited twice.
% In this case, the published CODECHECK certificate and possibly the published peer review can clearly describe the possibly large efforts put into both.

The codechecker
community\footnote{\href{https://github.com/codecheckers/codecheckers/}{https://github.com/codecheckers/codecheckers/}}
has over 20 volunteers who signed up in the last year.  Their
motivations, mentioned in the registration
information\footnote{\url{https://github.com/codecheckers/codecheckers/labels/registration}},
include: supporting reproducible research and Open Science, improve
coding skills, gaining experience in helping scientists with their
code, encouraging a sharing culture, and learning from other people's
mistakes; many are also motivated simply by curiosity.  We see
benefits to an open shared list of codecheckers across journals rather
than a private in-house group, as this may allow for better matches
regarding expertise and more even sharing of the workload.  Overall,
this community will aim to ensure that CODECHECK is a viable option
for independent no-cost Open Access journals.

@@

\textbf{4. Workflows must be auditable.} \\
The codechecker should have sufficient material to validate the
workflow outputs submitted by the
authors. Stark~\cite{stark_before_2018} calls this
``preproducibility'' and the ICERM report \cite{stodden_setting_2013}
defines the level ``Auditable Research'' similarly.  Every community
may establish their own good practices or adapt generic concepts and
practical tools, such as publishing all building blocks of science in
a research compendium
\footnote{\url{https://research-compendium.science/}}.  A completed
check means that code could be executed at least once using the
provided instructions, and, therefore, all code and data was given and
could be investigated more deeply or extended in the future.  Ideally,
this is a ``one~click'' step, but achieving this requires particular
skills and a sufficient level of documentation for third
parties. Furthermore, automation may lead to people gaming the system
or reliance on technology, which can often hide important details.
All such aspects can reduce the understandability of the material, so
we estimate our approach to codechecking, done without automation and
with open human communication, to be a simple way to ensure long-term
transparency and usefulness.  We acknowledge that others have argued
in favour of bitwise reproducibility because, in the long run, it can
be automated\footnote{Konrad Hinsen on Twitter:
  \url{https://twitter.com/khinsen/status/1242842759733665799}}, but
until then we need CODECHECK's approach.

@@

At the end of each CODECHECK, the codechecker writes a certificate
stating which outputs from the original article, i.e.,~numbers,
figures or tables, could be reproduced.  This certificate is made
openly available so that all readers of the article can see which
elements were reproduced and what limitations or issues were found.
The certificate links to code and data used by the codechecker,
allowing others to build on the work.  The format of the certificates
evolved during the project, as we have learnt to automate different
aspects of the certification, such as inserting figures into
certificate documents and managing metadata of a check.  The metadata
is stored in a machine-readable structured file in YAML, the CODECHECK
configuration file \texttt{codecheck.yml}\footnote{ See technical
  specification of the CODECHECK configuration file at
  \url{https://codecheck.org.uk/spec/config/latest/}.}.  The
configuration file enables current and future automation of workflows
and meta-analyses.

@@

We use freely available infrastructure, GitHub and Zenodo, to run our
system.  The \texttt{codecheckers} \textbf{GitHub}
organisation\footnote{ \url{https://github.com/codecheckers}} contains
projects for managing the project website, the codecheckers community
and its discussions, code repositories, and the main register of
CODECHECKs. Both the website\footnote{
  \url{https://codecheck.org.uk/}} and the register\footnote{
  \url{https://codecheck.org.uk/register}} are hosted as GitHub
pages. The register is a single table in CSV format that connects the
certificate identifier with the repository associated with a specific
conducted CODECHECK. Each of these repositories, which currently can
be hosted on GitHub or Open Science Framework (OSF), contains the
CODECHECK metadata file \texttt{codecheck.yml}. The register further
contains a column for the type of check, e.g.,~community, journal, or
conference, and the respective GitHub issue where communications and
assignments around a specific check are organised. No information is
duplicated between the register and the metadata files. The continuous
integration infrastructure of GitHub, GitHub Actions, is used to
automate the register for viewing (HTML) and for integration with
other services (CSV, JSON).  \textbf{Zenodo} is our preferred open repository for
storing certificates. It mints DOIs for deposits and ensures
long-term availability of all digital artefacts related to the
project. The CODECHECK community on Zenodo
\footnote{\url{https://zenodo.org/communities/codecheck/}} includes
certificates and the regularly archived register
\cite{codecheck_register_jan2021}.

@@

Fifteen RCR Reports have been published so far
\footnote{\url{https://search.crossref.org/?q=\%22Replicated+Computations+Results+\%28RCR\%29+Report\%22&from_ui=yes&page=2};
  search executed on 2020-12-10.}
% 15: https://academic.microsoft.com/search?q=Replicated%20Computations%20Results%20%22(RCR)%20Report%22&f=&orderBy=0&skip=10&take=10
and the process is being extended extended to the ACM journal
\emph{Transactions on Modeling and Computer Simulation
  (TOMACS)}\footnote{\url{https://dl.acm.org/journal/tomacs/author-guidelines}}.
The TOMS RCR follows CODECHECK principles 1-4, although our work was
independently developed of theirs.  Here, we discuss variants of
CODECHECK, while TOMS RCR realises one particular workflow for
reproducibility reviews for one particular journal. The TOMS editorial
\cite{heroux_editorial_2015} shares similar concerns about selection
of reviewers, as we discussed above. Unlike existing CODECHECK
certificates, the RCR reports, which are similar to CODECHECK
certificates, undergo editorial review, but this could eventually
become part of the CODECHECK processes at journals.  The publication
of the RCR report is seen as a reward for the efforts of the
reproducing person, while the potential for this motive to be a
conflict of interest is acknowledged.  TOMS also recognises reviewer
activity in a partnership with Publons\footnote{
  \url{https://authors.acm.org/author-services/publons}}.
%, but it is
unclear if the author of an RCR report receives both the report's
%authorship and the reviewer recognition. 
CODECHECK however specifically aims to give codecheckers
recognition as reviewers.  In our view, the reviewer role removes the
possible conflict of interest while keeping the public
acknowledgement.  Specific to the field of mathematics, the RCR is
also expected to apply a review of the software itself if the system
it runs on cannot be evaluated by an independent party.  The TOMS RCR
creators concur with the importance of communication, expect
collaboration between author and RCR reviewers, share the
considerations around reviewer selection, and also put trust in
reviewer judgement over numerical bit-wise perfection.  A key
difference is that for TOMS RCR, authors opt-in with an \emph{RCR
  Review Request} and the RCR reports are published in the TOMS
journal next to the actual papers.
%% SJE: think this could be tightened a bit, and some of it I don't
%% fully understand.

Several journals provide special article types for reproductions of
published papers.  \emph{Information Systems} has an
invited reproducibility paper track\footnote{
  \url{https://www.elsevier.com/journals/information-systems/0306-4379/guide-for-authors}.}.
\emph{Nature Machine Intelligence} recently introduced a new type of
article, the reusability report \cite{noauthor_research_2020}.
Inspired by the detailed and nuanced submissions to a reproducibility
challenge, the reusability report focuses on the exploration of
robustness and generalizability of the original paper's claims
\cite{noauthor_research_2020}. This answers the specific community's
challenges around computational reproducibility and also values these
kinds of contributions as independent publications, which goes beyond
the goals of CODECHECK.  The journal \emph{Cortex} has a special
article type \emph{Verification Reports}, which are actually about
replication of results and are very well designed/reasoned
\cite{chambers_verification_2020}.  In a similar vein, the CODECHECK
certificates could also be published as a special article type within
journals.

Going beyond article types and a specific journal, the journal
\emph{ReScience C} publishes only
replications\footnote{\url{https://rescience.github.io/faq/}}, also
requiring open code and replication by a third party. ReScience also
relies on free infrastructure (GitHub and Zenodo).

For research with very high stakes, where reproduction would be too weak and
post-publication replication possibly too late because of policy impact,
Benjamin-Chung et~al. \cite{benjamin-chung_internal_2020} propose
\emph{internal replication}.
A workflow that has undergone internal
replication would very likely be of high quality and relatively easy to check.
Similarly, internal CODECHECKs may be used, with the same limitations such
as group think \cite{benjamin-chung_internal_2020},
to ensure reproducibility before submission.
Such internal checks are professionalised in local reproduction services,
such as CISER R-squared\footnote{
\url{https://ciser.cornell.edu/research/results-reproduction-r-squared-service/}} (established/permanent),
%Uni Münster's Reproducible Research Support Service\footnote{
%\url{https://go.wwu.de/r2s2}} (pilot),
Oxford's code review network (OxCRN)\footnote{
\url{https://github.com/OxfordCodeReviewNet/forum}} (community, broader scope), or
Yale's YARD\footnote{
\url{https://isps.yale.edu/research/data/approach}} (staff for replications).

@@

Another platform for publishing results of reproductions is
\emph{SciGen.Report}\footnote{\url{https://scigen.report/}}.  It is a
community-run independent platform to foster communication on
reproducibility.  People can report on fully, partially, or
un-successful reproductions of articles after publication.

CODECHECK is uniquely designed to be adopted across journals or events
and to build a community of codecheckers. CODECHECK shares its
interdisciplinary nature with other community initiatives concerned
with reproducibility awareness, education, and support, such as
ReproHack\footnote{\url{https://reprohack.github.io/reprohack-hq/}},
Code Copilot\footnote{\url{https://twitter.com/Code_Copilot}}, or
Papers with Code\footnote{\url{https://paperswithcode.com/about}}.
The latter recently announced a collaboration with the preprint server
\emph{arXiv} on providing data and code supplements for machine
learning
manuscripts\footnote{\url{https://medium.com/paperswithcode/papers-with-code-partners-with-arxiv-ecc362883167}}
and runs a reproducibility
challenge\footnote{\url{https://paperswithcode.com/rc2020}}.
% Papers with Code now also does more disciplines than just ML.
Likewise, different disciplines and journals provide reproducibility
checklists, e.g.,~science and engineering \cite{rosenberg_next_2020} or
GIScience \cite{nust_agile_2019}, which naturally share some aspects
while addressing particularities as well as addressing researchers
from different fields. Regarding the education and guidance for
authors, we see CODECHECK's role as referencing and linking
educational efforts and helpful material, not as creating and
maintaining such content.

@@

\newpage

\textbf{Should CODECHECK requirements be more demanding?} \\
CODECHECK by design does not require authors to provide (and sustain)
an eternally functional workflow nor suggests a specific software
stack or practical approach even if such suggestions, e.g.,~research
compendia or ``repro-packs''\footnote{See
  \url{https://research-compendium.science/} respectively
  \cite{barba_praxis_2018}.}, are valuable.  Creating something
that anyone can reproduce has been called a fool's
errand\footnote{\url{https://twitter.com/DougBlank/status/1135904909663068165?s=09}}
and we tend to agree.  However, the package of data, code, and
documentation collaboratively created by authors and codecheckers is a
snapshot of a working analysis that greatly increases the likelihood
of a successful reproduction and the possibility that a workflow can
be extended by third parties in the future, as long as they have
access to suitable resources and matching skill set.  Concrete
implementations of CODECHECK workflows, especially for specific
disciplines, may reify much more helpful guidelines for authors on how
to create reproducibility packages.  Our author-friendly ``low bar''
should not stay low forever, but cultural change takes time and the
encouragement and guidance that CODECHECK, as part of the widely
accepted peer review concept, can provide may eventually allow the bar
to be raised much higher, e.g.,~with executable research
compendia \cite{nust_opening_2017}, ``Whole Tales''
\cite{brinckman_computing_2018}, or continuous analysis
\cite{beaulieu-jones_reproducibility_2017-1}.  However, considering
that missing artefacts and lack of documentation have repeatedly been
identified as key barriers to reproducibility
(e.g.,~\cite{stagge_assessing_2019,nust_improving_2020}), we would not
underestimate the power of a simple check.  For example, ModelDB
curation policies require that only one figure need be manually reproduced
\cite{mcdougal_reproducibility_2016}, but that has not limited the
usefulness nor success of the platform.

@@

\textbf{Shouldn't the next step be more revolutionary?}  CODECHECK's
approach is to acknowledge shortcomings around computational
reproducibility and to iteratively improve the current system.  It
remains to be proven whether this approach is welcomed broadly and if
involving publishing stakeholders helps to further the cause.  We have
discussed more stringent rules at length, e.g. only considering fully
free and open source software, diamond Open Access journals, but we
eventually decided against them on the level of the principles.  For
the CODECHECK community
process\footnote{\url{https://codecheck.org.uk/guide/community-process}}
and the volunteer codechecker community, these requirements are
reconsidered.

>>>>

Given that no clear standards yet exist for sharing data, what hope might there be for sharing computer programs?
Both data and software are required to validate a
computational analysis; data can be seen as inert whereas
code requires an environment to be run in.
This makes software harder to share.
Our experience is that researchers offer several reasons for why code
is not shared, e.g.,~``there is no documentation'', ``I cannot maintain it'', or ``I do not want to give away my code to competitors''.
Our view is that sharing code, wherever possible, is good for the community and the individual \cite{Barnes2010-iv,markowetz_five_2015}.
Having code and data openly available and archived provides a valuable
resource for others to learn from, even if the code is broken or lacks documentation.
However, with a little effort, we believe that if an independent person can execute an analysis, this is worth documenting and that this  reduces the barrier to evaluating non-text research materials.
Just as data journals' validations of data and all journals' peer review  provides a ``baseline reassurance'', i.e.,~that a paper has been checked by someone with an understanding of the topic \cite{fyfe_mission_2019}, the same baseline could be provided for the workflow underlying a paper.
With this in mind, we have developed a set of principles and an example workflow that provides a pragmatic way of checking that a paper's code works, i.e., it is reproducible following the Claerbout/Donoho/Peng terminology \cite{barba_terminologies_2018}.

Here we offer a thorough description of a process and its variations to integrate a much-needed evaluation of computational reproducibility into peer review, and we demonstrate its feasibility by means of 25 reproductions across scientific disciplines.
We call this system CODECHECK.

@@

\textbf{Step 3:} The CODECHECKER runs the code, based on instructions provided by
the author. They check if some or all of the results from the paper can be
reproduced. If there are
any problems running the code, the CODECHECKER asks the AUTHOR for help,
updates, or further documentation.
The burden to provide reproducible material lies with the author.
The CODECHECKER then tries to run the code again.
This process iterates until either the CODECHECKER is successful,
or the CODECHECKER concludes the code can not be executed within the context of a CODECHECK.
As part of this process, the CODECHECKER could work entirely locally, relying on their own computing resources, or in the cloud, e.g.,~using the open MyBinder infrastructure \cite{jupyter_binder_2018} or alternatives, some of which are more tailored to scientific publications while others offer commercial options for, e.g.,~publishers (cf. \cite{konkol_publishing_2020}).
A cloud-based infrastructure allows for the CODECHECKER and author to collaboratively improve the code and enforces a complete definition of the computing environment; but, unless secure infrastructure is provided, e.g.,~by the PUBLISHER, this requires the code and data to be published openly online.
Note that the task of the CODECHECKER is to check the ``mechanics'' of the workflow not to evaluate its correctness. 
In the context of mathematics, Stodden et~al. \cite{stodden_setting_2013} distinguish between \emph{verification} and \emph{validation};
following their definition, a CODECHECK ensures verification
%\footnote{Note this is a different use from that referred to as the \emph{Verification Reports} article type in the journal \emph{Cortex} \cite{chambers_verification_2020}.},
of computational results, i.e.,~checking that the code correctly produces the output it claims to create, but not a validation, i.e.,~checking that the code implements the right algorithm to solve the specific research problem.
Nevertheless, simply attempting to reproduce an output may highlight a submission's shortcomings in meeting a journal's requirements (cf.~\cite{christian_journal_2020}) and may effectively increase transparency, thereby improving practices (cf.~\cite{nosek_scientific_2012}) even if the check does not go into every detail.

@@

\textbf{Step 6:} The PUBLISHER can, depending on the timing, provide the
certificate to peer-reviewers or handling editors or publish it
and link between  certificate, paper, and any repositories 
through metadata. Currently, the CODECHECKER creates these connections on
Zenodo. They appear as links with a relationship type on the Zenodo
landing page for a record in the right-hand sidebar, e.g., the 
``related identifiers'' and ``alternate identifiers'' 
of certificate \texttt{2020-025} \cite{cert-2020-025}.
The PUBLISHER also credits the CODECHECKER for their work by depositing
the activity appropriately in scholarly profiles, such as ORCID
(see peer review contributions in ORCID records,
\url{https://support.orcid.org/hc/en-us/articles/360006971333-Peer-Review}).
The PUBLISHER also ensures proper publication metadata, e.g.,~links from the 
certificate repository to the published paper or the original code repository.

@@

We also see a great opportunity to involve \emph{early-career researchers} (ECRs) as codecheckers.
ECRs arguably have a high interest in learning
about the latest tools and technologies, as they build up their own
expertise and specialisation.
CODECHECK offers a way for ECRs to gain insights into new research and
highlight the importance of reproduction.  
\emph{ReScience X}, a journal devoted to reproduction and replication experiments \cite{roesch_new_2020}, shares an interest in this combination.
ECRs are also often familiar with new technologies, thus also making them likely to author CODECHECK-ready manuscripts.
A supporting data point for ECRs as early adopters is that they are responsible for 77\% of 141 registered reports that were submitted to leading Neuroscience \cite{chambers_registered_2019}.
As ECRs are introduced to peer review as codecheckers, they may transition into the role of scientific reviewer over time.
Overall, we see several opportunities and benefits to setting up a new process for CODECHECKING with a clear commitment to openness and transparency, independent of the current peer review process (see \emph{Openness} dimension).

The codechecker could be a member of \textbf{editorial staff}; this is
the most controlled but also resource-intensive option.  Such a
resource commitment would show that publishers are investing in
reproducibility, yet this commitment may be hard for small publishers.
These codecheckers could be fully integrated into internal workflows.
Credit for doing the codecheck is also achieved, as it is part of
their duties.  By contrast, it is useful for researchers to be
publicly credited for their reviewing activity.  A regular review
may be listed in public databases (e.g.,~ORCID, see Step~6 above,
or commercial offerings such as Publons, \url{https://publons.com/}, and
ReviewerCredits, \url{https://www.reviewercredits.com/});
a codechecker could be similarly listed.
% The number of scientific reviews is of course only a coarse indicator of an individual's community contribution, yet it is unclear if a regular reviewer, who conducts a regular scientific review and in addition also conducts a CODECHECK, should be credited twice.
% In this case, the published CODECHECK certificate and possibly the published peer review can clearly describe the possibly large efforts put into both.

The codechecker community has over 20 volunteers who signed up in the last
year, see \url{https://github.com/codecheckers/codecheckers/}.  Their
motivations, mentioned in the registration
information at \url{https://github.com/codecheckers/codecheckers/labels/registration},
include: supporting reproducible research and Open Science, improve
coding skills, gaining experience in helping scientists with their
code, encouraging a sharing culture, and learning from other people's
mistakes; many are also motivated simply by curiosity.  We see
benefits to an open shared list of codecheckers across journals rather
than a private in-house group, as this may allow for better matches
regarding expertise and more even sharing of the workload.  Overall,
this community will aim to ensure that CODECHECK is a viable option
for independent no-cost Open Access journals.

@@

\textbf{4. Workflows must be auditable.} \\
The codechecker should have sufficient material to validate the
workflow outputs submitted by the
authors. Stark~\cite{stark_before_2018} calls this
``preproducibility'' and the ICERM report \cite{stodden_setting_2013}
defines the level ``Auditable Research'' similarly.  Every community
may establish their own good practices or adapt generic concepts and
practical tools, such as publishing all building blocks of science in
a research compendium (cf.~\url{https://research-compendium.science/})
or ``repro-pack'' \cite{barba_praxis_2018}.
A completed
check means that code could be executed at least once using the
provided instructions, and, therefore, all code and data was given and
could be investigated more deeply or extended in the future.  Ideally,
this is a ``one~click'' step, but achieving this requires particular
skills and a sufficient level of documentation for third
parties. Furthermore, automation may lead to people gaming the system
or reliance on technology, which can often hide important details.
All such aspects can reduce the understandability of the material, so
we estimate our approach to codechecking, done without automation and
with open human communication, to be a simple way to ensure long-term
transparency and usefulness.  We acknowledge that others have argued
in favour of bitwise reproducibility because, in the long run, it can
be automated (e.g., Konrad Hinsen on Twitter,
\url{https://twitter.com/khinsen/status/1242842759733665799}), but
until then we need CODECHECK's approach.

@@

At the end of each CODECHECK, the codechecker writes a certificate
stating which outputs from the original article, i.e.,~numbers,
figures or tables, could be reproduced.  This certificate is made
openly available so that all readers of the article can see which
elements were reproduced and what limitations or issues were found.
The certificate links to code and data used by the codechecker,
allowing others to build on the work.  The format of the certificates
evolved during the project, as we have learnt to automate different
aspects of the certification, such as inserting figures into
certificate documents and managing metadata of a check.  The metadata
is stored in a machine-readable structured file in YAML, the CODECHECK
configuration file \texttt{codecheck.yml}.
The technical specification of the CODECHECK configuration file is
published at \url{https://codecheck.org.uk/spec/config/latest/}.  The
configuration file enables current and future automation of workflows
and meta-analyses.

@@

We use freely available infrastructure, GitHub and Zenodo, to run our
system.  The \texttt{codecheckers} \textbf{GitHub}
organisation at \url{https://github.com/codecheckers} contains
projects for managing the project website, the codecheckers community
and its discussions, code repositories, and the main register of
CODECHECKs. Both the project website \url{https://codecheck.org.uk/}}
and the register at \url{https://codecheck.org.uk/register}
are hosted as GitHub pages.
The register database is a single table in CSV format that connects the
certificate identifier with the repository associated with a specific
conducted CODECHECK. Each of these repositories, which currently can
be hosted on GitHub or Open Science Framework (OSF), contains the
CODECHECK metadata file \texttt{codecheck.yml}. The register further
contains a column for the type of check, e.g.,~community, journal, or
conference, and the respective GitHub issue where communications and
assignments around a specific check are organised. No information is
duplicated between the register and the metadata files. The continuous
integration infrastructure of GitHub, GitHub Actions, is used to
automate the register for viewing (HTML) and for integration with
other services (CSV, JSON).  \textbf{Zenodo} is our preferred open repository for
storing certificates. It mints DOIs for deposits and ensures
long-term availability of all digital artefacts related to the
project. The CODECHECK community on Zenodo is available at
\url{https://zenodo.org/communities/codecheck/}. It holds
certificates, the regularly archived register
\cite{codecheck_register_jan2021}, and other material related to
CODECHECK.

@@

Fifteen RCR Reports have been published so far (search on 
\url{https://search.crossref.org/} with the term
\texttt{"Replicated Computations Results (RCR) Report"} on 2020-12-10).
% 15: https://academic.microsoft.com/search?q=Replicated%20Computations%20Results%20%22(RCR)%20Report%22&f=&orderBy=0&skip=10&take=10
and the process is being extended extended to the ACM journal
\emph{Transactions on Modeling and Computer Simulation
  (TOMACS)} (cf. \url{https://dl.acm.org/journal/tomacs/author-guidelines}).
The TOMS RCR follows CODECHECK principles 1-4, although our work was
independently developed of theirs.  Here, we discuss variants of
CODECHECK, while TOMS RCR realises one particular workflow for
reproducibility reviews for one particular journal. The TOMS editorial
\cite{heroux_editorial_2015} shares similar concerns about selection
of reviewers, as we discussed above. Unlike existing CODECHECK
certificates, the RCR reports, which are similar to CODECHECK
certificates, undergo editorial review, but this could eventually
become part of the CODECHECK processes at journals.  The publication
of the RCR report is seen as a reward for the efforts of the
reproducing person, while the potential for this motive to be a
conflict of interest is acknowledged.  TOMS also recognises reviewer
activity in a partnership with Publons
(see \url{https://authors.acm.org/author-services/publons}).
It is unclear if the author of an RCR report receives both recognitions.
CODECHECK, however, specifically aims to give codecheckers
recognition as reviewers.  In our view, the reviewer role removes the
possible conflict of interest while keeping the public
acknowledgement.  Specific to the field of mathematics, the RCR is
also expected to apply a review of the software itself if the system
it runs on cannot be evaluated by an independent party.  The TOMS RCR
creators concur with the importance of communication, expect
collaboration between author and RCR reviewers, share the
considerations around reviewer selection, and also put trust in
reviewer judgement over numerical bit-wise perfection.  A key
difference is that for TOMS RCR, authors opt-in with an \emph{RCR
  Review Request} and the RCR reports are published in the TOMS
journal next to the actual papers.
%% SJE: think this could be tightened a bit, and some of it I don't
%% fully understand.

Several journals provide special article types for reproductions of
published papers.  \emph{Information Systems} has an invitation only
Reproducibility Section for articles describing the reproducibility 
efforts of published articles, which are co-authored by the original
authors and the reproducibility reviewer(s) (see
\url{https://www.elsevier.com/journals/information-systems/0306-4379/guide-for-authors}).
\emph{Nature Machine Intelligence} recently introduced a new type of
article, the reusability report \cite{noauthor_research_2020}.
Inspired by the detailed and nuanced submissions to a reproducibility
challenge, the reusability report focuses on the exploration of
robustness and generalizability of the original paper's claims
\cite{noauthor_research_2020}. This answers the specific community's
challenges around computational reproducibility and also values these
kinds of contributions as independent publications, which goes beyond
the goals of CODECHECK.  The journal \emph{Cortex} has a special
article type \emph{Verification Reports}, which are actually about
replication of results and are very well designed/reasoned
\cite{chambers_verification_2020}.  In a similar vein, the CODECHECK
certificates could also be published as a special article type within
journals.

Going beyond article types and a specific journal, the journal
\emph{ReScience C} (\url{https://rescience.github.io/}) publishes only
replications, also
requiring open code and replication by a third party. ReScience also
relies on free infrastructure (GitHub and Zenodo).

For research with very high stakes, where reproduction would be too weak and
post-publication replication possibly too late because of policy impact,
Benjamin-Chung et~al. \cite{benjamin-chung_internal_2020} propose
\emph{internal replication}.
A workflow that has undergone internal
replication would very likely be of high quality and relatively easy to check.
Similarly, internal CODECHECKs may be used, with the same limitations such
as group think \cite{benjamin-chung_internal_2020},
to ensure reproducibility before submission.
Such internal checks are professionalised in local reproduction services,
such as CISER R-squared
(\url{https://ciser.cornell.edu/research/results-reproduction-r-squared-service/})
or YARD (\url{https://isps.yale.edu/research/data/approach}),
or in communities such as Oxford's code review network (OxCRN,
\url{https://github.com/OxfordCodeReviewNet/forum}).

@@

Another platform for publishing results of reproductions is
\emph{SciGen.Report} (\url{https://scigen.report/}).  It is a
community-run independent platform to foster communication on
reproducibility.  People can report on fully, partially, or
un-successful reproductions of articles after publication.

CODECHECK is uniquely designed to be adopted across journals or events
and to build a community of codecheckers. CODECHECK shares its
interdisciplinary nature with other community initiatives concerned
with reproducibility awareness, education, and support, such as
ReproHack (\url{https://reprohack.github.io/reprohack-hq/}),
Code Copilot (\url{https://twitter.com/Code_Copilot}), or
Papers with Code (\url{https://paperswithcode.com/about}).
The latter recently announced a collaboration with the preprint server
\emph{arXiv} on providing data and code supplements for machine
learning manuscripts
%\footnote{\url{https://medium.com/paperswithcode/papers-with-code-partners-with-arxiv-ecc362883167}}
and runs a reproducibility challenge.
%\footnote{\url{https://paperswithcode.com/rc2020}}.
% Papers with Code now also does more disciplines than just ML.
Likewise, different disciplines and journals provide reproducibility
checklists, e.g.,~science and engineering \cite{rosenberg_next_2020} or
GIScience \cite{nust_agile_2019}, which naturally share some aspects
while addressing particularities as well as addressing researchers
from different fields. Regarding the education and guidance for
authors, we see CODECHECK's role as referencing and linking
educational efforts and helpful material, not as creating and
maintaining such content.

@@

\textbf{Should CODECHECK requirements be more demanding?} \\
CODECHECK by design does not require authors to provide (and sustain)
an eternally functional workflow nor suggests a specific software
stack or practical approach.
Creating something
that anyone can reproduce has been called a fool's
errand (Douglas Blank on Twitter,
\url{https://twitter.com/DougBlank/status/1135904909663068165})
and we tend to agree.  However, the package of data, code, and
documentation collaboratively created by authors and codecheckers is a
snapshot of a working analysis that greatly increases the likelihood
of a successful reproduction and the possibility that a workflow can
be extended by third parties in the future, as long as they have
access to suitable resources and matching skill set.  Concrete
implementations of CODECHECK workflows, especially for specific
disciplines, may reify much more helpful guidelines for authors on how
to create reproducibility packages.  Our author-friendly ``low bar''
should not stay low forever, but cultural change takes time and the
encouragement and guidance that CODECHECK, as part of the widely
accepted peer review concept, can provide may eventually allow the bar
to be raised much higher, e.g.,~with executable research
compendia \cite{nust_opening_2017}, ``Whole Tales''
\cite{brinckman_computing_2018}, or continuous analysis
\cite{beaulieu-jones_reproducibility_2017-1}.  However, considering
that missing artefacts and lack of documentation have repeatedly been
identified as key barriers to reproducibility
(e.g.,~\cite{stagge_assessing_2019,nust_improving_2020}), we would not
underestimate the power of a simple check.  For example, ModelDB
curation policies require that only one figure need be manually reproduced
\cite{mcdougal_reproducibility_2016}, but that has not limited the
usefulness nor success of the platform.

@@

\textbf{Shouldn't the next step be more revolutionary?}  CODECHECK's
approach is to acknowledge shortcomings around computational
reproducibility and to iteratively improve the current system.  It
remains to be proven whether this approach is welcomed broadly and if
involving publishing stakeholders helps to further the cause.  We have
discussed more stringent rules at length, e.g. only considering fully
free and open source software, diamond Open Access journals, but we
eventually decided against them on the level of the principles.  For
the CODECHECK community
process, which is documented online at
\url{https://codecheck.org.uk/guide/community-process},
and the volunteer codechecker community, these requirements are
reconsidered.
